Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-03 paper/ms.tex
Incorporate JNW suggestions (part 1)
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.43\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$ (brighter stars
    are larger). The \texttt{X} and \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale.  Two stars of
    interest are ``Star A'' and ``Star B'', which were eventually
    excluded as being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

\edit1{Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.

@@

Validating a transiting planet means statistically arguing that the
data are much more likely to be explained by a planet than by an
astrophysical false positive. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data {\it must} be explained by a planet, for instance
through combined photometric transits and a radial velocity mass
measurement.

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837. Combined with spectroscopic and
  imaging constraints, hierarchical eclipsing binary scenarios are
  ruled out.  Background eclipsing binary scenarios are limited by
  speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.43\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    White circles are neighboring stars with $T<16$ (brighter stars
    are larger). The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale.  Two stars of
    interest are ``Star A'' and ``Star B'', which were eventually
    excluded as being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

\edit1{Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.  Star B was not detected; with a separation of $5.4''$ from
\tn, it fell outside the field of view.

@@

Validating a transiting planet means statistically arguing that the
data are much more likely to be explained by a planet than by an
astrophysical false positive. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the transits {\it must} be explained by a planet, through
elimination of all false positive scenarios and determination that the
planety's mass is in the substellar regime.
